Preparing a manuscript for a peer-reviewed journal the FMDL way

### 2021-08-04 IITD_Manuscript.tex
Even clearer instructions regarding naming added.
Additional help for use of git added.
Updated acknowledgments with statement of contributions and CRediT taxonomy

Read through the entire PDF. This will tell you in which order to write the paper with cardinal order defined in bold, large red letters.

@@

There is an underlying philosophy to the way we do manuscripts in the lab - regardless of what it is, the name of the repo (already addressed in the README file), file, section, figure file, label to a figure, label to an equation, label to a table, etc. \textbf{\Huge \textcolor{red}{must reflect the contents of whatever is being referenced or named}}. Hopefully, Table~(\ref{tbl:namingthings}) will serve as a useful rolodex - it is not complete, but it is strongly indicative.

@@

Authors FA, TA, PS and MS declare competing interest in the form of an Indian patent application (2021345678).

>>>>

Read through the entire PDF. This will tell you in which order to write the paper with cardinal order defined in bold, large red letters. You also need to pay attention to the comments in the .tex file associated with this PDF.

@@

There is an underlying philosophy to the way we do manuscripts in the lab - regardless of what it is, the name of the repo (already addressed in the README file), file, section, figure file, label to a figure, label to an equation, label to a table, etc. \textbf{\Huge \textcolor{blue}{must reflect the contents of whatever is being referenced or named}}. Hopefully, Table~(\ref{tbl:namingthings}) will serve as a useful rolodex - it is not complete, but it is strongly indicative.

@@

\subsection{Statement of contributions}

FA fabricated the devices. FA and TA characterized devices. SA and PS synthesized active semiconductor materials. SA, TA, and PS carried out XPS measurements. FA, SA, TA, and PS carried out data reduction. FA, SA, PS, CP and MS carried out technical discussions. FA, SA, CP and MS wrote the manuscript.

As per \href{https://casrai.org/credit/}{CRediT} taxonomy: a) Conceptualization: FA, CP and MS, b) Data curation: FA, SA, TA, and PS, c) Formal analysis: FA and PS, d) Funding acquisition: CP and MS, e) Investigation: FA, SA, TA, and PS, f) Methodology: PS, CP and MS, g) Project administration: PS, CP and MS, h) Resources: CP and MS, i) Software: FA, SA and PS, j) Supervision: PS, CP and MS, k) Validation: FA and TA, l) Visualization: FA, SA, TA, and PS, m) Writing - original draft: FA and SA, n) Writing - review \& editing: CP and MS.

\subsection{Conflicts of Interest}
Authors FA, TA, PS and MS declare competing interest in the form of an Indian patent application (2021345678).
